---
title: "All-in-One Scirpt for Miniprep Development Analysis"
author: "Izzy Hernandez"
date: "February 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#### PART 1: Make a scatter plot of LB vs TB (+ Kanamycin) clone penalty scores (NGS Data) ####


#Import Data from Excel Workbook to plot
```{r}
#LB+Kanamycin Clones = 5-8
#TB+Kanamycin Clones = 9-12
#Penalty Scores divided by LB vs. TB

#use install.packages("readxl") if you don't have the package yet

library(readxl) #load library to import Excel Workbook into your R workspace
PenaltyData <- read_excel("C:/Users/ihernandez/Desktop/Molecular Bio Projects/Experiments and Data Analysis/Miniprep in TB LB/Experiment 2 - C040g/C040g_Datafor_Rscripts.xlsx", 
     sheet = "PenaltyScore_Plot")

#Workbook now loaded and saved as Penalty Data
#Can use head(LB_TB_CloneData_forR) to check first few entries of the data.

```


#Define Data for the X and Y axis of the plot (penalty scores for LB vs. TB + Kanamycin)
```{r}
LB_penalty <- PenaltyData$LB_penaltyscore #Will use for x axis
TB_penalty <- PenaltyData$TB_penaltyscore #Will use for y axis
```


#Make a simple scatter plot which correlates the penalty scores of LB+Kanamycin Clones with TB+Kanamycin Clones.
```{r}
#use install.packages("ggpplot2") if you don't have this install -- very useful for data visualization!

library(ggplot2) #load ggplot library
LB_TB_penaltygraph <- ggplot(PenaltyData, aes(x=LB_penalty, y=TB_penalty)) + geom_point()

LB_TB_penaltygraph + labs(title = "Correlation of LB+Kan and TB+Kan Penalty Scores", x = "LB+Kan Penalty Score", y = "TB+Kan Penalty Score") + geom_smooth(method = "lm") + theme_bw() + theme(plot.title = element_text(hjust = 0.5))
```




#### PART 2: Make Histograms of LB and TB Miniprep DNA Concentrations ####

#Import Data from Excel Workbook to plot
```{r}

library(readxl) #load library to import Excel Workbook into your R workspace
C040g_LBdna <- read_excel("C:/Users/ihernandez/Desktop/Molecular Bio Projects/Experiments and Data Analysis/Miniprep in TB LB/Experiment 2 - C040g/C040g_Datafor_Rscripts.xlsx", 
      sheet = "LB_KanHist")

```


#Define Data for DNA concentrations of LB Minipreps
```{r}
LB_DNAquant <- C040g_LBdna$`LB_Concentration` #Will use for x axis
```


#Make a simple historgram of LB+Kanamycin DNA concentrations
```{r}
library(ggplot2)
LB_DNA_Histogram <- ggplot(C040g_LBdna, aes(x=LB_DNAquant)) + geom_histogram(binwidth = 1, col = "black", fill="darkblue") #makes histogram of LB+Kan DNA quants
LB_DNA_Histogram+ labs(title = "Distribution of LB+Kan DNA Concentrations", x = "[DNA] (ng/uL)", y = "Count") + theme_bw() + theme(plot.title = element_text(hjust = 0.5))
```


#### Creating a Histogram of TB+Kan Miniprep DNA Concentrations ####
```{r}
library(readxl) #load library to import Excel Workbook into your R workspace
C040g_TBdna <- read_excel("C:/Users/ihernandez/Desktop/Molecular Bio Projects/Experiments and Data Analysis/Miniprep in TB LB/Experiment 2 - C040g/C040g_Datafor_Rscripts.xlsx", 
      sheet = "TB_KanHist")

```


#Define Data for DNA concentrations of TB + carb Minipreps
```{r}
TB_DNAquant <- C040g_TBdna$`TB_Concentration` #Will use for x axis
```


#Make a simple historgram of LB+Kanamycin DNA concentrations
```{r}
library(ggplot2)
TB_DNA_Histogram <- ggplot(C040g_TBdna, aes(x=TB_DNAquant)) + geom_histogram(binwidth = 2, col = "black", fill ="darkred")
TB_DNA_Histogram+ labs(title = "Distribution of TB+Kan DNA Concentrations", x = "[DNA] (ng/uL)", y = "Count") + theme_bw() + theme(plot.title = element_text(hjust = 0.5))
```




#### PART 3: Make a dotplot of LB vs. TB Miniprep DNA Concentrations ####

#Import Data from Excel Workbook to plot
```{r}

library(readxl) #load library to import Excel Workbook into your R workspace
C040g_QuantData <- read_excel("C:/Users/ihernandez/Desktop/Molecular Bio Projects/Experiments and Data Analysis/Miniprep in TB LB/Experiment 2 - C040g/C040g_Datafor_Rscripts.xlsx", 
      sheet = "Data_DNAConc_Plot")
#view(C040g_Datafor_Rscripts)
```


#Define Data for the X and Y axis of the plot (penalty scores for LB vs. TB + Kanamycin)
```{r}
LB_DNAquant <- C040g_QuantData$LB_Concentration #Will use for x axis
TB_DNAquant <- C040g_QuantData$TB_Concentration #Will use for y axis
```


#Make a simple scatter plot which correlates the penalty scores of LB+Kan Clones with TB+Kan Clones.
```{r}
library(ggplot2) #load ggplot library
LB_TB_concentrationgraph <- ggplot(C040g_QuantData, aes(x=LB_DNAquant, y=TB_DNAquant)) + geom_point() + scale_y_continuous(expand = c(0, 0), limits = c(0, 50)) + scale_x_continuous(expand = c(0, 0), limits = c(0, 20))  
LB_TB_concentrationgraph + labs(title = "Correlation of LB+Kan and TB+Kan DNA Concentrations", x = "LB+Kan [DNA] (ng/uL)", y = "TB+Kan [DNA] (ng/uL)") + geom_smooth(method = "lm") + theme_bw() + theme(plot.title = element_text(hjust = 0.5))
```
